\title{Marcell, Jason - Resume}
\author{Jason Marcell}
\documentclass[10pt]{article}
\usepackage{hyperref}
\usepackage[top=.5in, bottom=.5in, left=.5in, right=.6in]{geometry}
\pagenumbering{gobble}
\setlength{\tabcolsep}{0in}
\begin{document}
  \begin{center}
    \textbf{\LARGE Jason Marcell} \\
  http://jmarcell.com \\
  jasonmarcell@gmail.com \\
  \end{center}

  \vspace{0.5em}
  {\large \textbf{Experience}}

  \begin{itemize}

    
    \item
    \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{Software Engineer}, Amazon, Austin, TX & 01/2024 - Present \\
    \end{tabular*}
    \begin{itemize}
      
      \item Built an award-winning hackathon POC for enterprise procurement classification that was immediately funded for production; served as technical lead for a team of engineers and data scientists to evolve from an LLM prototype into a scalable classical ML pipeline on AWS SageMaker, now deployed to production processing millions of records with projected annual savings of roughly half a million dollars.
      
      \item Designed experimental AI-assisted development workflows using coordinated LLM subagents, tmux-orchestrated task graphs, git-worktrees, and ephemeral cloud environments to parallelize engineering workflows; built internal LLM-powered developer tooling integrating codebase context and operational runbooks.
      
      \item Early leader of an AI initiative across a 50+ engineer organization; created a 14-topic agentic AI workshop series, built internal AI agents and developer tooling, and drove adoption of AI-native development workflows across the department.
      
      \item Established a department-wide pattern for auto-generated SDKs from OpenAPI specifications, eliminating thousands of lines of manual integration code and standardizing API integrations across multiple systems.
      
    \end{itemize}
    
    \item
    \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{Lead Software Engineer}, Capital One, McLean, VA (Remote) & 11/2022 - 01/2024 \\
    \end{tabular*}
    \begin{itemize}
      
      \item Led a team building a modular ETL platform for large-scale financial forecasting on a fully serverless AWS stack (DynamoDB, Lambda, React).
      
      \item Developed open-source Jira CLI and inner-source Feature Toggle CLI adopted company-wide.
      
    \end{itemize}
    
    \item
    \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{Staff Software Engineer}, Twilio, San Francisco, CA (Remote) & 09/2021 - 11/2022 \\
    \end{tabular*}
    \begin{itemize}
      
      \item Led a team of eight engineers building Twilio's Lookup API, an industry-leading consumer trust and phone identity platform.
      
    \end{itemize}
    
    \item
    \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{Staff Software Engineer}, Lucid, LLC, New Orleans, LA & 05/2018 - 09/2021 \\
    \end{tabular*}
    \begin{itemize}
      
      \item Led engineering of new microservices in Python and Golang on AWS, contributing to the first billion-dollar startup acquisition in Louisiana.
      
    \end{itemize}
    
    \item
    \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{Software Engineer}, Apple, Inc., Cupertino, CA & 10/2011 - 05/2018 \\
    \end{tabular*}
    \begin{itemize}
      
      \item Safari and WebKit Operations — built CI/CD infrastructure, testing, and deployment tooling for Apple's browser engine across iPhone and Mac.
      
      \item Hardware Reliability Engineering — wrote software for automated hardware stress testing and large-scale data analysis that directly informed product development from prototype through launch.
      
    \end{itemize}
    

  \end{itemize}

  \vspace{0.5em}
  {\large \textbf{Skills}}

  \begin{flushleft}
    \addtolength{\leftskip}{.3in}

    \textbf{AI / ML:} Generative AI, LLM Applications, Agentic Workflows, Retrieval-Augmented Generation (RAG), Classical Machine Learning, AWS Bedrock, AWS SageMaker, scikit-learn

    \vspace{0.3em}

    \textbf{Languages:} Python, Java, Rust

    \vspace{0.3em}

    \textbf{Infrastructure:} AWS, Serverless Architecture (Lambda, DynamoDB, API Gateway), Docker, CI/CD, Infrastructure as Code (CloudFormation, CDK)

    \vspace{0.3em}

    \textbf{Systems Engineering:} AI-Native Development, Distributed Systems, REST APIs, OpenAPI, SDK Generation, Microservices, Test Automation
  \end{flushleft}

  \vspace{0.5em}
  {\large \textbf{Certifications}}
  \begin{itemize}
      
      \item AWS Certified Solutions Architect - Associate
      
      \item Eagle Scout, Boy Scouts of America
      
  \end{itemize}

  \vspace{0.5em}
  {\large \textbf{Education}}
  \begin{itemize}
    
    \item
      \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
        \textbf{Cornell University}, Masters of Engineering Computer Science & 08/2010 - 05/2011 \\
      \end{tabular*}
    
    \item
      \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
        \textbf{United States Marine Corps}, Officer Candidate School & 05/2003 - 06/2003 \\
      \end{tabular*}
    
    \item
      \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
        \textbf{Georgia Institute of Technology}, Bachelor of Science Electrical Engineering & 08/2000 - 07/2004 \\
      \end{tabular*}
    
  \end{itemize}

\end{document}